Incentivizing Exploration with Unbiased Histories

### 2019-02-01 COLT 2019 Submission/intro.tex
Minor edit.

\xhdr{Our results and discussion.}
Our main result is a transitive, unbiased-subhistory policy which attains near-optimal $\tilde{O}(\sqrt{T})$ regret rate for a constant number of actions. This policy also obtains the optimal instance-dependent regret rate
    $\tilde{O}(\tfrac{1}{\Delta})$
for problem instances with gap $\Delta$, without knowing the $\Delta$ in advance. In particular, we match the regret rate achieved for incentivizing exploration with unrestricted disclosure policies \cite{ICexploration-ec15-working}.

>>>>

\xhdr{Our results and discussion.}
Our main result is a transitive, unbiased-subhistory policy which attains near-optimal $\tilde{O}(\sqrt{T})$ regret rate for a constant number of actions. This policy also obtains the optimal instance-dependent regret rate
    $\tilde{O}(\tfrac{1}{\Delta})$
for problem instances with gap $\Delta$, without knowing the $\Delta$ in advance. In particular, we match the regret rate achieved for incentivizing exploration with unrestricted disclosure policies \citep{ICexploration-ec15-working}.
